---
title: "Comparison Between the Facebook Pages for Different Platforms"
author: "Jack Brewer, Aden Webb, Avebry Haughton-Vowles, Kacper Mazur"
date: "12 February 2018"
output: beamer_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(Rfacebook)
citation("Rfacebook")
library(stringr) # Character manipulation
library(dplyr) # Data wrangling
library(ggplot2) # Graphics
library(tidyr) # Turning wide data into long data
library(tm) # Text mining
library(wordcloud) # Word cloud
library(network) # Network diagram
library(curl) # Needed to get information about me and my friends
library(httr) # Needed to get information about me and my friends
library(lubridate) # For date manipulation
library(scales) # To format axes
library(wordcloud2)

#---Functions---

format.facebook.date <- function(datestring) {
  date <- as.POSIXct(datestring, 
                     format = "%Y-%m-%dT%H:%M:%S+0000", 
                     tz = "GMT")
  date
}

remove_http_www <- function(some_txt){
    #
    some_txt <- str_replace_all(some_txt, 
                                "http\\:\\/\\/[A-Za-z0-9\\.\\/\\?\\=]+(\\s?)", "")
    #
    some_txt <- str_replace_all(some_txt, 
                                "https\\:\\/\\/[A-Za-z0-9\\.\\/\\?\\=]+(\\s?)", "")
    # 
    some_txt <- str_replace_all(some_txt, 
                                "www\\.[A-Za-z0-9\\.\\/\\?\\=]+(\\s?)", "")
    #
    return(some_txt)
}

remove.numbers <- function(some_txt){
    # Remove separate numbers
    some_txt <- str_replace_all(some_txt, "\\s\\d+", " ") #
    #
    # Remove numbers in brackets
    some_txt <- str_replace_all(some_txt, "\\(\\d+\\)", "") 
    #
    # Remove numbers at the beginning
    some_txt <- str_replace_all(some_txt, "^\\d+\\s", "")
    #
    # Remove numbers at the end
    some_txt <- str_replace_all(some_txt, "\\s\\d+$", "")
    #
    some_txt
}

remove.spaces <- function(some_txt){
    # If more than one space, replace by one space
    some_txt <- str_replace_all(some_txt, "\\s{2,}", " ") 
    #
    # Remove beginning and ending spaces
    some_txt <-  str_replace_all(some_txt, "^\\s+|\\s+$", "")
    #
    some_txt
}

match_with_negation <- function(phrase, word_table, consider_negation = TRUE,
                                negation_dictionary = c("not", "isn't","aren't", "haven't","won't", "doesn't")){
    #
    # phrase is the phrase being considered
    # word_table is the dictionary of words in which we are looking for matches
    # consider_negation: if TRUE,
    # then the appearance of a negation word before a match is taken into account
    # negation_dictionary is a list of negation words (which we can add to)
    #
    # Obtain the individual words in phrase
    #
    individual_words <- unlist(str_split(phrase, '\\s+')) # Needs package stringr
    #
    # Remove the English articles as these can cause confusion when considering negation
    #
    individual_words <- individual_words[!individual_words %in% c("a", "the")]
    #
    # Where are the matches?
    # Position of the word in the word_table
    # If there is no match NA is reported
    #
    match_positions_in_table <- match(individual_words, word_table)
    #
    # So words that match are those that are not NA
    # Let's record which ones these are
    #
    match_positions_in_phrase <- which(!is.na(match_positions_in_table))
    #
    # How many matches?
    # This is the total number of elements that are not NA
    #
    number_of_matches <- sum(!is.na(match_positions_in_table))
    #
    # If we should take account of the appearance of a negation word before a match:
    #
    if(consider_negation){
        #
        # Position of preceding words
        #
        previous_words_position <- match_positions_in_phrase - 1
        #
        # Make sure that none of these are zero, as we can't index from zero
        #
        previous_words_position <- previous_words_position[previous_words_position > 0]
        #
        # What are those words?
        #
        previous_words <- individual_words[previous_words_position]
        #
        # Do they negate?
        #
        negation_words <- previous_words[previous_words %in% negation_dictionary]
        #
        # Remove the number of negation words from the number of matches
        #
        number_of_matches <- number_of_matches - length(negation_words)
        # So a phrase such as "not good" is recorded as neutral (score 0)
        # rather than 1 for the positive word "good"
    }
    #
    # Return the number of matches
    #
    number_of_matches
}

get.page.data <- function(page_name) {
  

}

pos <- scan("positive-words.txt", what = "character", comment.char = ";")
neg <- scan("negative-words.txt", what = "character", comment.char = ";")

token <- "EAACEdEose0cBALD6saZA0MvKRxxhYSMqsZCMUUz19rGfxFG2LIJVky46b5PuVZAeniPNhBfNZCJcuDNLLTvQVnkLqbNZBtiTExYYvwZBLdXE20Nzx28PrRvd8SZCPftVCl2KrajQOGHVq4UeTbunZAHRAPSIpXVQOMMMripZAJvYYWwxnwbksWKgpXV0cph3uV4DvwTrLRTfnXQZDZD"
```

## Introduction

We chose to do our presentation on the similarities and differences between various game platforms. We chose this as it is something we are familier with, due to us all being games development students, and it could be interesting to look at different variations of the same service.


## Chosen Pages

The three services we will be looking at are:

- Xbox
- Playstation
- Steam

We chose these as they are the most widely used platforms and so were likely to yield the most active FaceBook Pages.

## Xbox and Playstation

These two are both examples of console gaming platforms. They are usually cheaper to get into with a lower barrier of entry. There is a larger focus on major releases periodically throughout the year.

We chose to use two examples of consoles because they are in direct competition so there is the possiblility of analysing similarities and differences between the two.

## Steam

Steam was picked to compare against the two console platforms. It is the primary method for gaming on a PC and therefore tends to have a higher barrier for enrty as a PC can be more expensive up-front than a console. 

Steam also gets the major releases at distinct points throughout the year but has a much greater focus on smaller games releasing very rapidly; almost constantly.

## Playstation

```{r include=FALSE}

playstationPageName <- "PlayStation"
number_required <- 1000
dates <- seq(as.Date("2017/01/31"), as.Date("2018/01/31"), by = "day")
n <- length(dates) - 1
df_daily <- list()

for (i in 1:n){
  cat(as.character(dates[i]), " ")
  try(df_daily[[i]] <- getPage(playstationPageName, token,
                               n = number_required,
                               since = dates[i],
                               until = dates[i + 1],
                               reactions = TRUE,
                               api = "v2.9"))
  cat("\n")
}

playstationPage <- do.call(rbind, df_daily)

playstationPage <- playstationPage %>%
  mutate(datetime = format.facebook.date(created_time) )

head(playstationPage$datetime)

playstationPage <- playstationPage %>%
  mutate(month = format(datetime, "%Y-%m"))

head(playstationPage$month)

playstation_monthly_summaries_wide <- playstationPage %>%
  group_by(month) %>%
  summarize("Average likes" = mean(likes_count),
            "Average comments" = mean(comments_count),
            "Average shares" = mean(shares_count),
            "Number of posts" = n())

playstation_monthly_summaries <- playstation_monthly_summaries_wide %>%
  gather("Monthly_Quantity","Number", 2:5)
```

```{r echo=FALSE, warning=FALSE}
ggplot(playstation_monthly_summaries, 
       aes(x = month, 
           y = Number, 
           group = Monthly_Quantity, 
           colour = Monthly_Quantity)) +
  geom_line(lwd = 1.5) + 
  facet_wrap(~ Monthly_Quantity, scales = "free_y") + 
  theme(axis.text.x = element_text(size = 14, angle = 270, hjust = 0, vjust = 0.5),
        axis.text.y = element_text(size = 14), 
        axis.title.x = element_text(size = 16),
        axis.title.y = element_text(size = 16, angle = 270),
        strip.text.x = element_text(size = 14),
        title = element_text(size = 20), 
        legend.position = "none") + 
  labs(title = paste(playstationPageName, "Facebook Page"), 
       subtitle = "Monthly Quantity Across Posts",
       x = "Month", 
       y = "Number")
```

## Negative and Positive Words in the Playstation Comments

```{r include=FALSE}
playstationPage$message
playstationPage_existing_messages <- playstationPage %>% 
  filter(!is.na(message))
playstationPage_existing_messages <- playstationPage_existing_messages %>% 
  mutate(message_cleaned = remove_http_www(message))
playstationPage_existing_messages <- playstationPage_existing_messages %>% 
  mutate(message_cleaned = str_replace_all(message_cleaned, "[^[:alnum:]]",  " ") )
playstationPage_existing_messages <- playstationPage_existing_messages %>% 
  mutate(message_cleaned = str_replace_all(message_cleaned, "[\u4E00-\u9FFF]+",  " ") )
playstationPage_existing_messages <- playstationPage_existing_messages %>% 
  mutate(message_cleaned = str_replace_all(message_cleaned, "[\u3400-\u4DBF]+",  " ") )
playstationPage_existing_messages <- playstationPage_existing_messages %>% 
  mutate(message_cleaned = remove.numbers(message_cleaned))
playstationPage_existing_messages <- playstationPage_existing_messages %>% 
  mutate(message_cleaned = remove.spaces(message_cleaned))
playstationPage_existing_messages <- playstationPage_existing_messages %>% 
  mutate(message_cleaned =  tolower(message_cleaned))
playstationPage_existing_messages$message_cleaned

#Word Counts/Frequency
text_corpus <- Corpus(VectorSource(playstationPage_existing_messages$message_cleaned))
text_corpus

new.stopwords <- c("http", "https", "ps4", "playstation", "sony", "games")

tdm <- TermDocumentMatrix(text_corpus, 
                          control = list(stopwords = c(new.stopwords, 
                                                       stopwords(kind = "en"))))
tdm_matrix <- as.matrix(tdm)
dim(tdm_matrix)
tdm_matrix[1:25, 1:25]
word_count <- rowSums(tdm_matrix)
head(word_count)
word_count_df <- data.frame(word = names(word_count), freq = word_count)
word_count_ordered_df <- word_count_df %>% 
  arrange(desc(freq))
head(word_count_ordered_df)

N <- 8
ps_words_freq_limited <- word_count_ordered_df[1:N,]
ps_words_freq_limited <- ps_words_freq_limited %>% 
  mutate(word = factor(word, levels = word))
ps_words_freq_limited$word
```

```{r echo=FALSE}

g_w_b <- rep(c("darkblue", "white", "black"), length = N)
ggplot(ps_words_freq_limited, 
       aes(x = word, 
           y = freq)) +
  geom_col(fill = g_w_b, colour = "black", alpha = 0.9) + 
  # colour refers to the edge of the bars        
  # values of alpha less than 1 cause transparency
  labs(title = paste("Most Common Words - ", playstationPageName),
       x = paste("Top", N, "Words"), 
       y = "Frequency") + 
  theme(axis.text = element_text(size = 14, color = "black"), 
        axis.title = element_text(size = 18, color = "black"),
        title = element_text(size = 20))
     
```

## Playstation psitivity value

```{r include=FALSE}

playstation_existing_messages_with_sentiments <- playstationPage_existing_messages %>% 
  rowwise() %>% 
  mutate(pos = match_with_negation(message_cleaned, pos), # Positive matches
         neg = match_with_negation(message_cleaned, neg), # Negative matches
         score = pos - neg) %>%
  ungroup()
playstation_existing_messages_with_sentiments %>% select(pos, neg, score) %>% head()
playstation_existing_messages_with_sentiments <- playstation_existing_messages_with_sentiments %>% 
  mutate(playstationPageName = playstationPageName)
playstation_existing_messages_with_sentiments %>% select(pos, neg, score, playstationPageName) %>% head()
playstation_existing_messages_with_sentiments %>% count(score)
playstation_sentiment_means <- playstation_existing_messages_with_sentiments %>% 
  summarize(playstation_mean_score = mean(score)) 

```

```{r echo=FALSE}
ggplot(playstation_existing_messages_with_sentiments, 
       aes(x = score)) +
  geom_bar() + 
  geom_vline(aes(xintercept = playstation_mean_score), data = playstation_sentiment_means) +
  geom_text(aes(x = playstation_mean_score, 
                y = Inf, 
                label = signif(playstation_mean_score, 3)),
            vjust = 2, 
            data = playstation_sentiment_means) + 
  scale_x_continuous(breaks = -10:15,  
                     minor_breaks = NULL) + 
  labs(title = paste("Sentiments towards", playstationPageName , "give a mean of", signif(playstation_sentiment_means$playstation_mean_score, 3)),
       x = "Sentiment Score (positive minus negative matches)" , 
       y = "Number of posts") + 
  theme()
```

## Steam

```{r include=FALSE}
steamPageName <- "Steam"

number_required <- 1000 

dateToUse <- "2018/01/31"

dates <- seq(as.Date("2017/01/31"), as.Date(dateToUse), by = "day")
dates

n <- length(dates) - 1
n

df_daily <- list()

for (i in 1:n){
  
  cat(as.character(dates[i]), " ") 
  
  try(df_daily[[i]] <- getPage(steamPageName, token, 
                               n = number_required, 
                               since = dates[i], 
                               until = dates[i + 1], 
                               reactions = TRUE,
                               api = "v2.9")) 
  
  cat("\n")
}

steamPage <- do.call(rbind, df_daily)

steamPage <- steamPage %>% 
  mutate(datetime = format.facebook.date(created_time) )

head(steamPage$datetime)

steamPage <- steamPage %>% 
  mutate(month = format(datetime, "%Y-%m"))

steam_monthly_summaries_wide <- steamPage %>%
  group_by(month) %>%
  summarize("Average likes" = mean(likes_count),
            "Average comments" = mean(comments_count),
            "Average shares" = mean(shares_count),
            "Number of posts" = n())

steam_monthly_summaries <- steam_monthly_summaries_wide %>% 
  gather("Monthly_Quantity","Number", 2:5) 
```

```{r echo=FALSE}
ggplot(steam_monthly_summaries, 
       aes(x = month, 
           y = Number, 
           group = Monthly_Quantity, 
           colour = Monthly_Quantity)) +
  geom_line(lwd = 1.5) + # Specify line width 
  facet_wrap(~ Monthly_Quantity, scales = "free_y") + # Use a free scale on the y-axis
  theme(axis.text.x = element_text(size = 14, angle = 270, hjust = 0, vjust = 0.5), # For rotated labels
        axis.text.y = element_text(size = 14), 
        axis.title.x = element_text(size = 16),
        axis.title.y = element_text(size = 16, angle = 270),
        strip.text.x = element_text(size = 14),
        title = element_text(size = 20), 
        legend.position = "none") + 
  labs(title = paste(steamPageName, "Facebook Page"), # Note the use of paste to create a title of the page name followed by some text (see below)
       subtitle = "Monthly Quantity Across Posts",
       x = "Month", 
       y = "Number") 

```

## Negative and Positive Words in the Steam Comments

```{r include=FALSE}
steam_existing_messages <- steamPage %>% 
  filter(!is.na(message))
steam_existing_messages <- steam_existing_messages %>% 
  mutate(message_cleaned = remove_http_www(message))
steam_existing_messages <- steam_existing_messages %>% 
  mutate(message_cleaned = str_replace_all(message_cleaned, "[^[:alnum:]]",  " ") )
steam_existing_messages <- steam_existing_messages %>% 
  mutate(message_cleaned = str_replace_all(message_cleaned, "[\u4E00-\u9FFF]+",  " ") )
steam_existing_messages <- steam_existing_messages %>% 
  mutate(message_cleaned = str_replace_all(message_cleaned, "[\u3400-\u4DBF]+",  " ") )
steam_existing_messages <- steam_existing_messages %>% 
  mutate(message_cleaned = remove.numbers(message_cleaned))
steam_existing_messages <- steam_existing_messages %>% 
  mutate(message_cleaned = remove.spaces(message_cleaned))
steam_existing_messages <- steam_existing_messages %>% 
  mutate(message_cleaned =  tolower(message_cleaned))
steam_existing_messages$message_cleaned

#Word Counts/Frequency
text_corpus <- Corpus(VectorSource(steam_existing_messages$message_cleaned))
text_corpus

new.stopwords <- c("http", "https", "steam", "valve", "pc")

tdm <- TermDocumentMatrix(text_corpus, 
                          control = list(stopwords = c(new.stopwords, 
                                                       stopwords(kind = "en"))))
tdm_matrix <- as.matrix(tdm)
dim(tdm_matrix)
tdm_matrix[1:25, 1:25]
word_count <- rowSums(tdm_matrix)
head(word_count)
word_count_df <- data.frame(word = names(word_count), freq = word_count)
steam_word_count_ordered_df <- word_count_df %>% 
  arrange(desc(freq))
head(word_count_ordered_df)

N <- 8
steam_words_freq_limited <- steam_word_count_ordered_df[1:N,]
steam_words_freq_limited <- steam_words_freq_limited %>% 
  mutate(word = factor(word, levels = word))
steam_words_freq_limited$word
```


```{r echo=FALSE}
bg <- rep(c("gray0", "gray25", "gray50"), length = N)
ggplot(steam_words_freq_limited, 
       aes(x = word, 
           y = freq)) +
  geom_col(fill = bg, colour = "black", alpha = 0.9) + 
  # colour refers to the edge of the bars        
  # values of alpha less than 1 cause transparency
  labs(title = paste("Most common words in post to page", steamPageName),
       x = paste("Top", N, "Words"), 
       y = "Frequency") + 
  theme(axis.text = element_text(size = 13, color = "black"), 
        axis.title = element_text(size = 18, color = "black"),
        title = element_text(size = 20))
```

## Steam Positivity Value

```{r include=FALSE}

steam_existing_messages_with_sentiments <- steam_existing_messages %>% 
  rowwise() %>% 
  mutate(pos = match_with_negation(message_cleaned, pos), # Positive matches
         neg = match_with_negation(message_cleaned, neg), # Negative matches
         score = pos - neg) %>%
  ungroup()
steam_existing_messages_with_sentiments %>% select(pos, neg, score) %>% head()
steam_existing_messages_with_sentiments <- steam_existing_messages_with_sentiments %>% 
  mutate(steamPageName = steamPageName)
steam_existing_messages_with_sentiments %>% select(pos, neg, score, steamPageName) %>% head()
steam_existing_messages_with_sentiments %>% count(score)
steam_sentiment_means <- steam_existing_messages_with_sentiments %>% 
  summarize(steam_mean_score = mean(score)) 

```

```{r echo=FALSE}
ggplot(steam_existing_messages_with_sentiments, 
       aes(x = score)) +
  geom_bar() + 
  geom_vline(aes(xintercept = steam_mean_score), data = steam_sentiment_means) +
  geom_text(aes(x = steam_mean_score, 
                y = Inf, 
                label = signif(steam_mean_score, 3)),
            vjust = 2, 
            data = steam_sentiment_means) + 
  scale_x_continuous(breaks = -10:15,  
                     minor_breaks = NULL) + 
  labs(title = paste("Sentiments towards", steamPageName , "give a mean of", signif(steam_sentiment_means$steam_mean_score, 3)),
       x = "Sentiment Score (positive minus negative matches)" , 
       y = "Number of posts") 
```

##Xbox

```{r include=FALSE}
xboxPageName <- "xbox"
number_required <- 1000
Sys.Date()
dates <- seq(as.Date("2017/01/31"), as.Date("2018/01/31"), by = "day")
n <- length(dates) - 1
df_daily <- list()
#
for (i in 1:n){
  cat(as.character(dates[i]), " ") 
  try(df_daily[[i]] <- getPage(xboxPageName, token, 
                               n = number_required, 
                               since = dates[i], 
                               until = dates[i + 1], 
                               reactions = TRUE,
                               api = "v2.9"))
  cat("\n")
}
#
xboxPage <- do.call(rbind, df_daily)
# Facebook Stats

xboxPage <- xboxPage %>% 
  mutate(datetime = format.facebook.date(created_time) )
head(xboxPage$datetime)
xboxPage <- xboxPage %>% 
  mutate(month = format(datetime, "%Y-%m"))
head(xboxPage$month)
xbox_monthly_summaries_wide <- xboxPage %>%
  group_by(month) %>%
  summarize("Average likes" = mean(likes_count),
            "Average comments" = mean(comments_count),
            "Average shares" = mean(shares_count),
            "Number of posts" = n())

xbox_monthly_summaries <- xbox_monthly_summaries_wide %>% 
  gather("Monthly_Quantity","Number", 2:5) 
xbox_monthly_summaries
```

```{r echo=FALSE}
ggplot(xbox_monthly_summaries, 
       aes(x = month, 
           y = Number, 
           group = Monthly_Quantity, 
           colour = Monthly_Quantity)) +
  geom_line(lwd = 1.5) + # Specify line width 
  facet_wrap(~ Monthly_Quantity, scales = "free_y") + 
  theme(axis.text.x = element_text(size = 14, angle = 270, hjust = 0, vjust = 0.5), 
        axis.text.y = element_text(size = 14), 
        axis.title.x = element_text(size = 16),
        axis.title.y = element_text(size = 16, angle = 270),
        strip.text.x = element_text(size = 14),
        title = element_text(size = 20), 
        legend.position = "none") + 
  labs(title = paste(xboxPageName, "Facebook Page"), 
       subtitle = "Monthly Quantity Across Posts",
       x = "Month", 
       y = "Number") 
```

## Negative and Positive Words in the Xbox Comments

```{r include=FALSE}
xbox_existing_messages <- xboxPage %>% 
  filter(!is.na(message))
xbox_existing_messages <- xbox_existing_messages %>% 
  mutate(message_cleaned = remove_http_www(message))
xbox_existing_messages <- xbox_existing_messages %>% 
  mutate(message_cleaned = str_replace_all(message_cleaned, "[^[:alnum:]]",  " ") )
xbox_existing_messages <- xbox_existing_messages %>% 
  mutate(message_cleaned = str_replace_all(message_cleaned, "[\u4E00-\u9FFF]+",  " ") )
xbox_existing_messages <- xbox_existing_messages %>% 
  mutate(message_cleaned = str_replace_all(message_cleaned, "[\u3400-\u4DBF]+",  " ") )
xbox_existing_messages <- xbox_existing_messages %>% 
  mutate(message_cleaned = remove.numbers(message_cleaned))
xbox_existing_messages <- xbox_existing_messages %>% 
  mutate(message_cleaned = remove.spaces(message_cleaned))
xbox_existing_messages <- xbox_existing_messages %>% 
  mutate(message_cleaned =  tolower(message_cleaned))

text_corpus <- Corpus(VectorSource(xbox_existing_messages$message_cleaned))
new.stopwords <- c("http", "https", "youtube", "xbox", "microsoft") 
tdm <- TermDocumentMatrix(text_corpus, 
                          control = list(stopwords = c(new.stopwords, 
                                                       stopwords(kind = "en"))))
tdm_matrix <- as.matrix(tdm)
tdm_matrix[1:25, 1:25]
word_count <- rowSums(tdm_matrix)
head(word_count)
word_count_df <- data.frame(word = names(word_count), freq = word_count)
word_count_ordered_df <- word_count_df %>% 
  arrange(desc(freq))
head(word_count_ordered_df)
N <- 8
xbox_words_freq_limited <- word_count_ordered_df[1:N,]
xbox_words_freq_limited <- xbox_words_freq_limited %>% 
  mutate(word = factor(word, levels = word))
xbox_words_freq_limited$word

```

```{r echo=FALSE}
#plots
#-----------------------------
#
col <- rep(c("limegreen", "white"), length = N)

ggplot(xbox_words_freq_limited, 
       aes(x = word, 
           y = freq)) +
  geom_col(fill = col) + 
  labs(title = paste("Most common words in post to page", xboxPageName),
       x = paste("Top", N, "Words"), 
       y = "Frequency") + 
  theme(axis.text = element_text(size = 13, color = "black"), 
        axis.title = element_text(size = 18, color = "black"),
        title = element_text(size = 20))
```

## Xbox Positivity Value

```{r include=FALSE}

xbox_existing_messages_with_sentiments <- xbox_existing_messages %>% 
  rowwise() %>% 
  mutate(pos = match_with_negation(message_cleaned, pos), # Positive matches
         neg = match_with_negation(message_cleaned, neg), # Negative matches
         score = pos - neg) %>%
  ungroup()
xbox_existing_messages_with_sentiments %>% select(pos, neg, score) %>% head()
xbox_existing_messages_with_sentiments <- xbox_existing_messages_with_sentiments %>% 
  mutate(xboxPageName = xboxPageName)
xbox_existing_messages_with_sentiments %>% select(pos, neg, score, xboxPageName) %>% head()
xbox_existing_messages_with_sentiments %>% count(score)
xbox_sentiment_means <- xbox_existing_messages_with_sentiments %>% 
  summarize(xbox_mean_score = mean(score)) 

```

```{r echo=FALSE}
ggplot(xbox_existing_messages_with_sentiments, 
       aes(x = score)) +
  geom_bar() + 
  geom_vline(aes(xintercept = xbox_mean_score), data = xbox_sentiment_means) +
  geom_text(aes(x = xbox_mean_score, 
                y = Inf, 
                label = signif(xbox_mean_score, 3)),
            vjust = 2, 
            data = xbox_sentiment_means) + 
  scale_x_continuous(breaks = -10:15,  
                     minor_breaks = NULL) + 
  labs(title = paste("Sentiments towards", xboxPageName , "give a mean of", signif(xbox_sentiment_means$xbox_mean_score, 3)),
       x = "Sentiment Score (positive minus negative matches)" , 
       y = "Number of posts") 
```

## Possible Explanation for Differing Words and Moods

From the cmoparisons of the words used in posts for each company, we can see some distinct themes becoming clear.

- Steam words tend to focus on new things and anything that might be upcoming. There is also a focus on sales as this is a alrge part of steams business strategy.

- Playstation appers to do a similar thing with words like "new" and "upcoming", drawing attenion to the new games that are coming to their platform.

- Xbox however seems to take a different approach. Among the most common words are things like "mature" or "rating". This shows that the company may be more open with the ratings of their games and try to make sure to sell them to the right audience. It could also show an increased level of formality (including required information)

## Number of comments over a year (all 3)

```{r include=FALSE}
abc <- c(xbox_monthly_summaries_wide$`Average comments`, steam_monthly_summaries_wide$`Average comments`, playstation_monthly_summaries_wide$`Average comments`)


namess <- c("xbox", "steam", "playstation")
namess_f <- factor(namess)

df <- data.frame(abc, namess_f)
df


```

```{r echo=FALSE}
ggplot(df , aes(x = namess_f, y = abc)) +
  geom_boxplot() +
  labs(title = "Box Plots to Show the Number of Comments", x = "Company Name", y = "Number of Comments") + 
  theme(axis.text = element_text(size = 13, color = "black"), 
        axis.title = element_text(size = 13, color = "black"),
        title = element_text(size = 16))
```

## Comment numbers explained

From these boxplots we can see that xbox has the most regular number of comments over the year, while having slightly more on average then the othe two.

Playstation has a much wider variation in the number of its comments - potentially meaning a larger number of "interactive posts" such as giveaways. These one off events would lead to very high outliers in the number of comments on a post.

Steam lies somewhere between the two, with some larger outliers.


## Likes over a year

```{r include=FALSE}

playlikes <- playstationPage$likes_count
xboxlikes <- xboxPage$likes_count
steamlikes <- steamPage$likes_count

playstationPage <- playstationPage %>% 
  mutate(datetime = format.facebook.date(created_time) )

playstationPage <- playstationPage%>% 
  mutate(month = format(datetime, "%Y-%m"))

playstationPage <- select(playstationPage, likes_count, month)
playstationPage

xboxPage <- xboxPage %>% 
  mutate(datetime = format.facebook.date(created_time) )

xboxPage <- xboxPage%>% 
  mutate(month = format(datetime, "%Y-%m"))

xboxPage <- select(xboxPage, likes_count, month)
xboxPage

steamPage <- steamPage %>% 
  mutate(datetime = format.facebook.date(created_time))

steamPage <- steamPage%>% 
  mutate(month = format(datetime, "%Y-%m"))

steamPage <- select(steamPage, likes_count, month)
steamPage

steamPage$tag <- 1
xboxPage$tag <- 2
playstationPage$tag <- 3


factor_1 <- function(x){
  factor(x,
         levels = c(1,2,3), labels = c("Steam", "Xbox", "Playstation"))
}

steamPage <- collect(steamPage)
playstationPage <- collect(playstationPage)
xboxPage <- collect(xboxPage)

monthly_summaries_wide_steam <- steamPage %>%
  group_by(month) %>%
  summarize("Average likes" = mean(likes_count))

monthly_summaries_wide_xbox <- xboxPage %>%
  group_by(month) %>%
  summarize("Average likes" = mean(likes_count))

monthly_summaries_wide_playstation <- playstationPage %>%
  group_by(month) %>%
  summarize("Average likes" = mean(likes_count))

monthly_summaries_wide_steam$tag <- 1
monthly_summaries_wide_xbox$tag <- 2
monthly_summaries_wide_playstation$tag <- 3

monthly_summaries_wide_steam <- monthly_summaries_wide_steam %>% mutate_at(.vars = vars(3), .funs = funs(factor_1))
monthly_summaries_wide_playstation <- monthly_summaries_wide_playstation %>% mutate_at(.vars = vars(3), .funs = funs(factor_1))
monthly_summaries_wide_xbox <- monthly_summaries_wide_xbox %>% mutate_at(.vars = vars(3), .funs = funs(factor_1))

combined <- data.frame(monthly_summaries_wide_steam)
combined <- rbind.data.frame(monthly_summaries_wide_playstation, monthly_summaries_wide_xbox, monthly_summaries_wide_steam)
combined
```

```{r echo=FALSE}
ggplot(combined, aes(x = month, y = `Average likes`, col = tag, group = tag)) +
  geom_point() +
  geom_line() +
  labs(x = "Month", y = "Average number of likes") +
  theme(axis.text = element_text(size = 7, color = "black"), 
        axis.title = element_text(size = 13, color = "black"),
        title = element_text(size = 16))
```

## Correlations

- Xbox
```{r}
cor(xbox_monthly_summaries_wide$`Average likes`, xbox_monthly_summaries_wide$`Average comments`)
```
From this value we can see a fairly strong positive correlation between likes and comments on the xbox facebook page.

- Playstation
```{r}
cor(playstation_monthly_summaries_wide$`Average likes`, playstation_monthly_summaries_wide$`Average comments`)
```
This is a fairly positive correlation but it is the lowest of the three. This shows that people tend to either like or comment on the facebook page.


## Correlations Continued

- Steam
```{r}
cor(steam_monthly_summaries_wide$`Average likes`, steam_monthly_summaries_wide$`Average comments`)
```
Steam has the strongest correlation between comments and likes. This shows that of the three pages steam has the most users which will like a post when they comment rather than one or the other. 

## Potential conclusion to be drawn

As we can see from the early graphs for each page, they all have an overall increase in post numbers during the course of a year. 

Xbox has less posts than some of the other pages, but has a very high rate of interaction with their posts. This shows a success for their marketing as they have the fewest posts making the largest interest.

Playstation has a very large number of posts each month and also a very large rate of interaction. This is another method which also works in the companies favour - it may however be a greater impact on the companies resources.

## Conclusions continued

Steam has a very low number of posts compared to the other two. It is not a significantly smaller company so therefore this shows that the company must be relying on other platforms and online communities. Steam is built for pc gamers, and those who game on a computer don't tend to interact with facebook as steam has its own chat system and social media aspects.

Playstation and Xbox do not have this additional social media aspect so they are reliant on other platforms (such as facebook)

## T-test Comparing Likes Between Steam and Xbox

The following t-test will be to determine whether or not the number of likes on these two pages are statistically different.

The null hypothesis for this test is that the values are not significantly different. This means that the hypothsis is that the values are different between the two pages.

if p value is smaller that 0.05 there is a difference 
```{r include=FALSE, include=FALSE, r include=FALSE}
likes_df = data.frame(steam_monthly_summaries_wide$`Average likes`, xbox_monthly_summaries_wide$`Average likes`)

colnames(likes_df)[1] <- "SteamAverage"
colnames(likes_df)[2] <- "XboxAverage"

likes_df_long <- likes_df %>% gather("PageName", "LikesNumber", 1:2)

likes_df_long

```

## P value 
```{r echo=FALSE, echo=FALSE, r echo=FALSE}
t.test(likes_df_long$LikesNumber ~ likes_df_long$PageName, data = likes_df_long, var.equal = TRUE)$p.value
```

From this P-Value we can see that there is a statistical difference between the likes count for steam and Xbox. This in turn means that our analysis of the likes count is valid as they are different enough to be compared.

## T-test Comparing Likes Between Playstation and Xbox

The following t-test will be to determine whether or not the number of likes on these two pages are statistically different.

The null hypothesis for this test is that the values are not significantly different. This means that the hypothsis is that the values are different between the two pages.

if p value is smaller that 0.05 there is a difference 
```{r include=FALSE, include=FALSE, r include=FALSE}
likes_df = data.frame(playstation_monthly_summaries_wide$`Average likes`, xbox_monthly_summaries_wide$`Average likes`)

colnames(likes_df)[1] <- "PlaystationAverage"
colnames(likes_df)[2] <- "XboxAverage"

likes_df_long <- likes_df %>% gather("PageName", "LikesNumber", 1:2)

likes_df_long

```

## P value 
```{r echo=FALSE, echo=FALSE, r echo=FALSE}
t.test(likes_df_long$LikesNumber ~ likes_df_long$PageName, data = likes_df_long, var.equal = TRUE)$p.value
```

From this P-Value we can see that there is no statistical difference between the likes count for Playstation and Xbox. This means that for the sake of any of our comparisons Xbox and Playstation are to be considered the same.

## T-test Comparing Likes Between Playstation and Steam

The following t-test will be to determine whether or not the number of likes on these two pages are statistically different.

The null hypothesis for this test is that the values are not significantly different. This means that the hypothsis is that the values are different between the two pages.

if p value is smaller that 0.05 there is a difference 
```{r include=FALSE, include=FALSE, r include=FALSE}
likes_df = data.frame(playstation_monthly_summaries_wide$`Average likes`, steam_monthly_summaries_wide$`Average likes`)

colnames(likes_df)[1] <- "PlaystationAverage"
colnames(likes_df)[2] <- "SteamAverage"

likes_df_long <- likes_df %>% gather("PageName", "LikesNumber", 1:2)

likes_df_long

```

## P value 
```{r echo=FALSE, echo=FALSE, r echo=FALSE}
t.test(likes_df_long$LikesNumber ~ likes_df_long$PageName, data = likes_df_long, var.equal = TRUE)$p.value
```

From this P-Value we can see that there is a statistical difference between the likes count for Playstation and Steam. This means that our arguments and comparisons are considered statistically valid.


